\begin{thebibliography}{00}
	\bibitem{b1} Xilinx Design Language Version 1.6, Xilinx, Inc., July 2000, Xilinx ISE 6.1i Documentation in ise6.1i/help/data/xdl.
	\bibitem{b2} J. Goeders, T. Gaskin, and B. Hutchings, ``Demand driven assembly of FPGA configurations usign partial reconfiguration, ubuntu linux, and PYNQ,'' ...	
	\bibitem{b3} C. Lavin, M. Padilla, J. Lamprecht, P. Lundrigan, B. Nelson, and B. Hutchings, ``RapidSmith: Do-It-Yourself CAD Tools for Xilinx FPGAs,'' in 2011 21st International Conference on Field Programmable Logic and Applications, Sept 2011, pp. 349–355.
	\bibitem{b4} N. Steiner, A. Wood, H. Shojaei, J. Couch, P. Athanas, and M. French, ``Torc: Towards an Open-source Tool Flow,'' in Proceedings of the 19th ACM/SIGDA International Symposium on Field Programmable Gate Arrays (FPGA ’11), February 2011, pp. 41–44.
	\bibitem{b5} L. Doolittle and L. Vincenzo, Vhd2vl, 20-Sep-2015. [Online]. Available: http://doolittle.icarus.com/~larry/vhd2vl/.
	\bibitem{b6} T. Haroldsen, B. Nelson and B. Hutchings, ``Packing a modern Xilinx FPGA using RapidSmith,'' 2016 International Conference on ReConFigurable 
	Computing and FPGAs (ReConFig), Cancun, 2016, pp. 1-6.
	\bibitem{b7} N. Shah and J. Rose, ``On the difficulty of pin-to-wire routing in FPGAs,'' 22nd International Conference on Field Programmable Logic and Applications (FPL), Oslo, 2012, pp. 83-90.
	\bibitem{b8} C. Ebeling, L. McMurchie, S. A. Hauck and S. Burns, ``Placement and routing tools for the Triptych FPGA,'' in IEEE Transactions on Very Large Scale Integration (VLSI) Systems, vol. 3, no. 4, pp. 473-482, Dec. 1995.
	\bibitem{b9} B. White and B. Nelson, ``Tincr – A Custom CAD Tool Framework for Vivado,'' in 2014 International Conference on ReConFigurable Computing and FPGAs (ReConFig14), Dec 2014, pp. 1–6.
	\bibitem{b10} T. Haroldsen, B. Nelson, and B. Hutchings, ``Rapidsmith 2: A framework	for bel-level cad exploration on xilinx fpgas,'' in Proceedings of the 2015 ACM/SIGDA International Symposium on Field-Programmable Gate Arrays. ACM, 2015, pp. 66–69.
	\bibitem{b11} T. Townsend and B. Nelson, ``Vivado design interface: An export/import capability for Vivado FPGA designs,'' 2017 27th International Conference on Field Programmable Logic and Applications (FPL), Ghent, 2017, pp. 1-7.
	\bibitem{b12} C. Wolf and J. Glaser, ``Yosys - A Free Verilog Synthesis Suite,'' in Proceedings of the 21st Austrian Workshop on Microelectronics (Austrochip). 2013.
	
\end{thebibliography}

Improving the Effectiveness of TMR Applications on FPGAs with an SEU-Aware Incremental Placement Technique FCCM 2018? - Not publicly available yet
C.  Wolf. Yosys Open SYnthesis Suite. http://www.clifford.at/yosys/. url: http://www.clifford.at/yosys/ (visited on 03/10/2016)
vhdl2verilog: http://www.edautils.com/vhdl2verilog.html